Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-12 doc/report/msc-report.tex
more on cardinality, and removed an incorrect passage on the row key.

TODO: -- Limits on cardinality --

[What are the limits of our system? How high cardinality do we support? (This
is closely tied to hbase and the qualifier-limit.) If Martin is going to have
\textit{normalized\_path} as one of his dimensions, we might run into trouble.]

@@

It was decided that the row keys should consist of unit and time-stamp. This
would keep related data within close range, e.g. all rows with the same unit
would be stored next to each other. This means reading data with different units
would imply expensive jumps within the stored data. Because of this it was
decided that queries only support a single unit to be queried.

@@

TODO: add summary on cardinality limits on cardinality here.

>>>>

Because of the distributed nature of HBase and its ability to store a very large
number of rows, there is no actual upper bound on the cardinality supported by
Zohmg. There may however be complex queries that have filters on
high-cardinality that Zohmg will be unable to answer. This can be remedied in
part by setting up projections that cater especially to those queries, but the
issue can not be fully avoided. The authors have successfully stored data where
the cardinality of the dimensions exceeded millions.

@@

@@
